cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-16 paper-cardinalR.Rmd
Started working on trefoil projections

trefoil3d_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.75, 0.7), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

trefoil3d_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.65), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

trefoil3d_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.62), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

>>>>

proj_obj1 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.04))

trefoil3d_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-1.2, 1.2), 
  title = "b1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

proj_obj2 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.04))

trefoil3d_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-1, 1.2), 
  title = "b2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

@@

proj_obj3 <- get_projection(projection = projection, 
                            proj_scale = 1.2, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.8,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.016))

trefoil3d_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-1, 0.8), 
  title = "b3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)
